%Acknowledgements are the author's statement of gratitude to and
%recognition of the people and institutions who helped the author's
%research and writing.

\begin{center}
\vspace*{52pt}
{\Large \textbf{ACKNOWLEDGEMENTS}}
\end{center}

I'm glad this is the part of the thesis that people like to read because I have many thanks to share. First, thank you to my advisor, Peter. Thank you for always treating me like a scientist, and not a student. I think that a trait of a great advisor is their willingness to work collaboratively with their students, and Peter does this incredibly well. Thank you for always being positive about results (even if no positivity was warranted), for providing suggestions, and for allowing me to work on whatever I wanted to. Thank you for helping me through `existential angst' and for supporting me in whatever career path I wanted to take. Thank you for always making sure there was a grant to pay my salary and for all of the meetings and Slack conversations. I will forever remember to ignore the gong and how one good result is already more than most of the literature. I am forever grateful for all of your support.

Next, thank you to my pseudo second advisor, Marc. Thank you for always reading my write ups and papers and always having great questions and suggestions. I always admire how successful, creative, and humble you are (oh and a great sense of humor). Thank you for all of the time and Monday meetings. The Monday meetings with Peter and Roland are some of my best memories. 

Thank you to Saray and Dane who have played an important role in mentoring me as a beginning grad student and helping me to write my first paper. Dane, thank you for your very detailed editing and notation considerations. I will forever remember the suggestions you made on the first paper. Saray, I am so lucky to work with you and even more lucky to have you as a friend. I rarely have met people that I can communicate with through eye contact. Our entropy together made everything more fun, from yard time, to `getting a mix', to flying with the random physicist to Zarzagoza (said with the Spanish accent) and eating way too much at Weaver Street. 

Thank you to my committee members, Jeremy, Tamara, Laura and David. Jeremy, thank you for being my first introduction to research in grad school. I will always remember p53 signaling dynamics and microRNAs. Tamara, I am so happy that I got to take your class in my second year, which inspired me so much and even made me wish I could switch to computer vision. You are a great role model as a smart and creative researcher. Laura and David, thank you for all of your suggestions in committee meetings and for reading this thesis.

I have been lucky to interact with a lot of great people over the years in the Mucha research group. Thanks to Nishant, Wayne, Sam, Howdy, Clara, Eun, Peter D, Nic, and Sean for brightening up Chapman.

Thank you to the people who make BCB run- Tim Elston, Will Valdar, and John Cornett. I know you all work very hard for BCB and I think we have a great group of creative students. We all owe so much gratitude to John Cornett who is always friendly, positive, responsive, and on top of things. I am also lucky to have met great friends in BCB who I have done homework with, looked up to, and gotten advice from. Thank you, Bryan, Dan, Greg, and Paul. 

Thanks to living in Chapel Hill, I was fortunate to make some incredible friends. To my super strong (literally strong) lady friends Jess, Mimi, and Libby: Thank you for all the nights we spent laughing and climbing. These are some of the best times. Thank you Andrew for being the most incredible nerd friend and one of the kindest people I have ever met. I can always count on you for awesome conversation. 

Last but not least, I owe a huge amount of gratitude to my family. First to my parents Pat and Eric who have supported me every day of my life. They have never put any pressure on me to do anything and support all of my dreams unconditionally. Most importantly, they are really friendly and fun people. I couldn't choose better parents. Thank you for tolerating my un responded text messages, my inability to mail a letter or find a stamp, and for helping me through tough times. Next to my brother, Mike. I admire you so much for always following your dreams and doing what feels right to you. Aside from being great at everything you do, you are such a kind, wonderful person. I hope you don't find any mistakes in this thesis or ask about consistency. 

Finally, thank you Thomas for supporting me in every possible way. I'm so happy that grad school lead me to you. You have enhanced my life in every way and inspire me every day to be a scientist. I am so lucky to have a great role model who works so hard, is so talented, and so kind. Thank you for always pushing me pursue things I didn't think that I could. Thank you for always telling me `shhhhhhh' when I started to get stressed. You are my favorite Dub.

OK, this is the end. Thank you everyone that read to the end.   

\clearpage
